---
title: "Time Series Forecasting - Modeltime and Slidy"
date: '`r format(Sys.Date(), "%B %d, %Y")`<br>• c - table of contents (bottom left) <br>• k - disable click to next slide<br>• use arrow keys to navigate'
author: "Tyler Otto"
output: slidy_presentation
---

```{r setup, include=FALSE}

knitr::opts_knit$set(root.dir = "~/Modeltime/modeltimeandslidy")

# Libraries ---------------------------------------------------------------
currentDate <- Sys.Date() 

library(readxl)
library(modeltime)
library(tidymodels)
library(tidyverse)
library(timetk)
library(lubridate)
library(zoo)
library(glue)
library(kableExtra)
library(tidyselect)
library(earth)
library(glmnet)
library(gt)

Sample_Superstore <- read_excel("Sample - Superstore.xls")

```


# Overview

* 5 types of models will be built and the best fit version of each model will be chosen an the champion for each type.

|         - Linear Regression Model
|         - ARIMA (Autoregressive Integrated Moving Average)
|         - GLMNET (Lasso and Elastic-Net Regularized Generalized Linear Models)
|         - Earth/MARS (Multivariate Adaptive Regression Spline)
|         - ETS (Exponential Smoothing)

* Models are chosen based on aggregating the accuracy measures and choosing the one with the least errors

* Modeltime documentation: https://business-science.github.io/modeltime/


# Time Series Testing - Consumer Segment Sales

```{r echo=FALSE, fig.height=7, fig.width=17,fig.align="center", message=FALSE, warning=FALSE}

assess_time <-  "12 months"
forecasted_months <-  "12 months"
select_segment <-  "Consumer"
source('build_models.R'
       # ,echo = TRUE
       # , print.eval = TRUE
       )


test_set_plot
accuracy_table
  
```

# Time Series Forecast - Consumer Segment Sales

```{r fig.width=17, fig.height=7, message=FALSE, warning=FALSE, echo=FALSE}

forecast_plot

forecast_compare_table

  
```

# Time Series Testing - Corporate Segment Sales

```{r echo=FALSE, fig.height=7, fig.width=17,fig.align="center", message=FALSE, warning=FALSE}

assess_time <-  "12 months"
forecasted_months <-  "12 months"
select_segment <-  "Corporate"
source('build_models.R'
       # ,echo = TRUE
       # , print.eval = TRUE
       )


test_set_plot
accuracy_table
  
```

# Time Series Forecast - Corporate Segment Sales

```{r fig.width=17, fig.height=7, message=FALSE, warning=FALSE, echo=FALSE}

forecast_plot

forecast_compare_table

```

# Time Series Testing - Home Office Segment Sales

```{r echo=FALSE, fig.height=7, fig.width=17,fig.align="center", message=FALSE, warning=FALSE}

assess_time <-  "12 months"
forecasted_months <-  "12 months"
select_segment <-  "Home Office"
source('build_models.R'
       # ,echo = TRUE
       # , print.eval = TRUE
       )


test_set_plot
accuracy_table
  
```

# Time Series Forecast - Home Office Segment Sales

```{r fig.width=17, fig.height=7, message=FALSE, warning=FALSE, echo=FALSE}

forecast_plot

forecast_compare_table
```
